On exponential sums arising from the classical doubling method

### 2025-02-28 paper.tex
Update paper.tex

We will assume that $\dim_{\finiteField} \hermitianSpace$ is even. This is automatic for all case, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.

>>>>

We will assume that $\dim_{\finiteField} \hermitianSpace$ is even. This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.
